Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling

### 2020-05-08 report/report.tex
Change nodes to edges in result tables

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 26473         & 10523        & 3044        & 2756        \\
    Nodes, total            & 6382579       & 6612383      & 968420      & 420810      \\
    Edge length, total      & 129984.79 km  & 186089.55 km & 29304.57 km & 16162.95 km \\
    Features, colliding     & 3189          & 1032         & 412         & 456         \\
    Nodes, colliding        & 7330          & 2362         & 643         & 824         \\
    Edge length, colliding  & 110.67 km     & 66.18 km     & 9389.30 m   & 20.41 km    \\
    Features, percent       & 12.05 \%      & 9.81 \%      & 13.53 \%    & 16.55 \%    \\
    Nodes, percent          & 0.11 \%       & 0.04 \%      & 0.07 \%     & 0.20 \%     \\
    Edge length, percent    & 0.09 \%       & 0.04 \%      & 0.03 \%     & 0.13 \%

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, colliding     & 134           & 336          & 246         & 277         \\
    Nodes, colliding        & 157           & 530          & 306         & 407         \\
    Edge length, colliding  & 3248.73       & 6475.99 m    & 3840.00 m   & 8039.54 m   \\
    Features, percent       & 0.51 \%       & 3.19 \%      & 8.08 \%     & 10.51 \%    \\
    Nodes, percent          & 0.00 \%       & 0.00 \%      & 0.03 \%     & 0.09 \%     \\
    Edge length, percent    & 0.00 \%       & 0.00 \%      & 0.01 \%     & 0.05 \%

>>>>

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, total         & 26473         & 10523        & 3044        & 2756        \\
    Edges, total            & 6382579       & 6612383      & 968420      & 420810      \\
    Edge length, total      & 129984.79 km  & 186089.55 km & 29304.57 km & 16162.95 km \\
    Features, colliding     & 3189          & 1032         & 412         & 456         \\
    Edges, colliding        & 7330          & 2362         & 643         & 824         \\
    Edge length, colliding  & 110.67 km     & 66.18 km     & 9389.30 m   & 20.41 km    \\
    Features, percent       & 12.05 \%      & 9.81 \%      & 13.53 \%    & 16.55 \%    \\
    Edges, percent          & 0.11 \%       & 0.04 \%      & 0.07 \%     & 0.20 \%     \\
    Edge length, percent    & 0.09 \%       & 0.04 \%      & 0.03 \%     & 0.13 \%

@@

\begin{table}[H]
\begin{tabular}{lllll}
                            & Footpath      & Residential  & Secondary   & Primary     \\
    Features, colliding     & 134           & 336          & 246         & 277         \\
    Edges, colliding        & 157           & 530          & 306         & 407         \\
    Edge length, colliding  & 3248.73       & 6475.99 m    & 3840.00 m   & 8039.54 m   \\
    Features, percent       & 0.51 \%       & 3.19 \%      & 8.08 \%     & 10.51 \%    \\
    Edges, percent          & 0.00 \%       & 0.00 \%      & 0.03 \%     & 0.09 \%     \\
    Edge length, percent    & 0.00 \%       & 0.00 \%      & 0.01 \%     & 0.05 \%
